Discrete Ordinates

### 2017-05-18 docprep/chapbib.tex
Updated a table

\begin{table}[ht]
\caption{Water Regions}
\centering 
\begin{tabular}{l c r r r r r r r r r r r r}
\hline \hline   
Media       & CT Range      & H    & C    & N    & 0    & Na  & Mg & P    & S   & Cl  & Ar  & K   & Ca \\ [0.5ex] 
\hline
Air         & -950 to -100  &      &      & 75.7 & 23.3 &     &    &      &     &     & 1.3 &     &       \\
Lung        & -1000 to -950 & 10.3 & 10.5 & 3.1  & 74.9 & 0.2 &    & 0.2  & 0.3 & 0.3 &     & 0.2 &       \\
Adipose     & -100 to 15    & 11.2 & 50.8 & 1.2  & 36.4 & 0.1 &    &      & 0.1 & 0.1 &     &     &       \\
Connective  & 15 to 129     & 10.0 & 16.3 & 4.3  & 68.4 & 0.4 &    &      & 0.4 & 0.3 &     &     &       \\
Bone        & 129 to 200    & 9.7  & 44.7 & 2.5  & 35.9 &     &    & 2.3  & 0.2 & 0.1 &     & 1.0 & 4.5   \\  [1ex]
\hline
\end{tabular}
\label{table:ctmap}
\end{table}

>>>>

\begin{table}[ht]
\caption{Water Regions}
\centering 
\begin{tabular}{l c r r r r r r r r r r r r}
\hline \hline   
Media       & CT Range      & H    & C    & N    & 0    & Na  & Mg  & P    & S   & Cl  & Ar  & K   & Ca \\ [0.5ex] 
\hline
Air         & -950 to -100  &      &      & 75.7 & 23.3 &     &     &      &     &     & 1.3 &     &      \\
Lung        & -1000 to -950 & 10.3 & 10.5 &  3.1 & 74.9 & 0.2 &     &  0.2 & 0.3 & 0.3 &     & 0.2 &      \\
Adipose     & -100 to 15    & 11.2 & 50.8 &  1.2 & 36.4 & 0.1 &     &      & 0.1 & 0.1 &     &     &      \\
Connective  & 15 to 129     & 10.0 & 16.3 &  4.3 & 68.4 & 0.4 &     &      & 0.4 & 0.3 &     &     &      \\
Bone 1      & 129 to 200    &  9.7 & 44.7 &  2.5 & 35.9 &     &     &  2.3 & 0.2 & 0.1 &     & 1.0 &  4.5 \\ 
Bone 2      & 200 to 300    &  9.1 & 41.4 &  2.7 & 36.8 &     & 0.1 &  3.2 & 0.2 & 0.1 &     & 1.0 &  6.3 \\ 
Bone 3      & 300 to 400    &  8.5 & 37.8 &  2.9 & 37.9 &     & 0.1 &  4.1 & 0.2 & 0.1 &     & 1.0 &  8.2 \\ 
Bone 4      & 400 to 500    &  8.0 & 34.5 &  3.1 & 38.8 &     & 0.1 &  5.0 & 0.2 & 0.1 &     & 1.0 & 10.0 \\ 
Bone 5      & 500 to 600    &  7.5 & 31.6 &  3.2 & 39.7 &     & 0.1 &  5.8 & 0.2 & 0.1 &     &     & 11.6 \\ 
Bone 6      & 600 to 700    &  7.1 & 28.7 &  3.4 & 40.4 &     & 0.1 &  6.6 & 0.2 & 0.1 &     &     & 13.1 \\ 
Bone 7      & 700 to 800    &  6.7 & 26.7 &  3.5 & 41.2 &     & 0.2 &  7.2 & 0.3 &     &     &     & 14.4 \\ 
Bone 8      & 800 to 900    &  6.3 & 24.7 &  3.7 & 41.8 &     & 0.2 &  7.8 & 0.3 &     &     &     & 15.7 \\ 
Bone 9      & 900 to 1000   &  6.0 & 22.7 &  3.8 & 42.4 &     & 0.2 &  8.4 & 0.3 &     &     &     & 16.8 \\ 
Bone 10     & 1000 to 1100  &  5.6 & 20.7 &  3.9 & 43.0 &     & 0.2 &  8.9 & 0.3 &     &     &     & 17.9 \\ 
Bone 11     & 1100 to 1200  &  5.3 & 18.7 &  4.0 & 43.5 &     & 0.2 &  9.4 & 0.3 &     &     &     & 18.9 \\ 
Bone 12     & 1200 to 1300  &  5.1 & 16.7 &  4.1 & 44.0 &     & 0.2 &  9.9 & 0.3 &     &     &     & 19.8 \\
Bone 13     & 1300 to 1400  &  4.8 & 15.7 &  4.2 & 44.4 &     & 0.2 & 10.3 & 0.3 &     &     &     & 20.7 \\
Bone 14     & 1400 to 1500  &  4.6 & 13.7 &  4.2 & 44.9 &     & 0.2 & 10.7 & 0.3 &     &     &     & 21.5 \\  
Bone 15     & > 1500        &  4.3 & 12.7 &  4.3 & 45.3 &     & 0.2 & 11.1 & 0.3 &     &     &     & 22.2 \\[1ex]
\hline
\end{tabular}
\label{table:ctmap}
\end{table}

### 2017-05-18 docprep/chapmeth.tex
Updated a table

\begin{table}[ht]
\caption{User Defined Quadrature Format}
\centering 
\begin{tabular}{c c c c}
\hline \hline   
$\mu$    & $\eta$ & $\xi$ & Weight\\ [0.5ex] 
\hline
5.12345  & 5.12345 & 5.12345 & 5.12345 \\
5.12345  & 5.12345 & 5.12345 & 5.12345 \\
5.12345  & 5.12345 & 5.12345 & 5.12345 \\
5.12345  & 5.12345 & 5.12345 & 5.12345 \\
5.12345  & 5.12345 & 5.12345 & 5.12345 \\
5.12345  & 5.12345 & 5.12345 & 5.12345 \\
5.12345  & 5.12345 & 5.12345 & 5.12345 \\
5.12345  & 5.12345 & 5.12345 & 5.12345 \\ [1ex]
\hline
\end{tabular}
\label{table:quad_format}
\end{table}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/airwaterxs1_19group}
        \caption{Data}
        \label{fig:ampx1}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/airwaterxs2_19group}
        \caption{Same data.}
        \label{fig:ampx2}
    \end{subfigure}
    \caption{Comparison to NIST data.}\label{fig:airwaterxs_19group}
\end{figure}

@@

\subsection{Multileaf Collimator}
How fancy.

Talk about the MCNP generation in the comparison to results part.

\section{Dose Computation}
Dose is computed.

>>>>

However, user defined directions \textit{should not} be parallel to any major axis. Doing so may result in undefined behavior. Also, after normalizaiton, no two rows should have identical values for $\mu$, $\eta$, and $\xi$ such as the last two rows of Table~\ref{tab:quad_interp}. Also, no weights can be negative.

\begin{table}[ht]
\caption{User Defined Quadrature Input}
\centering 
\begin{tabular}{c c c c}
\hline \hline   
$\mu$    & $\eta$ & $\xi$ & Weight\\ [0.5ex] 
\hline
1        & 0      & 0      & 1 \\
0.999    & 0.001  & 0.001  & 1 \\
1.0      & 1.0    & 1.0    & 1.3 \\
0.02198  & 0.2987 & .34520 & .02226 \\
.001     & .001   & .999   & 0.999 \\
-1       & 1      & -1     & .2 \\
-1.2     & 1.2    & -1.2   & 0.1 \\
1        & -1     & -1     & .2 \\ [1ex]
\hline
\end{tabular}
\label{tab:quad_format}
\end{table}

\begin{table}[ht]
\caption{User Defined Quadrature Interpretation}
\centering 
\begin{tabular}{c c c c}
\hline \hline   
$\mu$    & $\eta$ & $\xi$ & Weight\\ [0.5ex] 
\hline
1.0000   & 0.0000 & 0.0000 & 0.2074 \\
0.999    & 0.001  & 0.001  & 0.2074 \\
1.0      & 1.0    & 1.0    & 0.2696 \\
0.02198  & 0.2987 & .34520 & 0.0207 \\
.001     & .001   & .999   & 0.0046 \\
1        & -1     & -1     & 0.2072 \\
-1.2     & 1.2    & -1.2   & 0.0415 \\
-1       & 1      & -1     & 0.0415 \\ [1ex]
\hline
\end{tabular}
\label{tab:quad_interp}
\end{table}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/airwaterxs2_19group}
        \caption{19 group data}
        \label{fig:airwaterxs2_19group}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/airwaterxs2_47group}
        \caption{47 group data.}
        \label{fig:airwaterxs2_47group}
    \end{subfigure}
    \caption{Comparison of the group-averaged DOCTORS cross section data to continuous NIST data.}\label{fig:airwaterxs_group}
\end{figure}

@@

\section{Dose Computation}
Dose can be computed in either one of two ways. The first way is to compute the spatial energy dependent fluence distribution and multiply by a fluence-to-dose conversion factor from ICRP 116 [CITE]. The second way to compute dose is to compute the energy deposition in each cell.

\subsection{Fluence-to-dose Conversion}

The publications of the ICRP include fluence-to-dose conversion factors for a reference phantom from various particle types and patient orientations. For CT systems, the rotationally symmetric (ROT) orientation is the most appropriate since the beam rotates about the patient.

This methodology is very simplistic and can be computed quickly with no extra (memory) overhead. When DOCTORS finishes running, the flux is multiplied by the photon

\begin{figure}[tb]
  \begin{center}
   \includegraphics[width=3.75in]{figs/icrp116_rotconv}
  \end{center}
  \caption{Fluence-to-dose conversion factors from ICRP 116 for photons.}
\label{fig:icrp116_rotconv}
\end{figure}

\subsection{Energy Deposition}

blah
